Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-15 article.tex
Scrapped lines

We run \verb;pirouette; (listing~\ref{lst:pir_run}) 
and plot the results (listing~\ref{lst:pir_plot}),
as shown in figure~\ref{fig:example_2}.
In this case, the inference model with a JC69 site model, 
strict clock model and Yule tree prior has the highest likelihood
amongst all candidates (table \ref{tab:evidences_example_2} shows
the evidences).

@@

The alignment
generated for the true tree had most evidence for the JC site model,
strict clock model and Yule tree prior, 
with a weight of 0.981 (as 
shown in table \ref{tab:evidences_example_4}). 
The alignment
generated for the twin tree had most evidence for the JC site model,
RLN clock model and CBS tree prior,
with a weight of 0.707 (as 
shown in table \ref{tab:evidences_example_4}).

@@

We run \verb;pirouette; (listing~\ref{lst:pir_run}) 
and plot the results (listing~\ref{lst:pir_plot}).
The output is shown in figure~\ref{fig:example_5}.
The alignment
generated from the true tree had most evidence for the JC site model,
strict clock model and Yule tree prior, 
with a weight of 0.981 \richel{again} (as 
shown in table \ref{tab:evidences_example_5}). 
The alignment
generated for the twin tree had most evidence for the JC site model,
RLN clock model and CBS tree prior,
with a weight of 0.707 \richel{again} (as 
shown in table \ref{tab:evidences_example_5_twin}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interpretation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We run \verb;pirouette; (listing~\ref{lst:pir_run}) 
and plot the results (listing~\ref{lst:pir_plot}),
as shown in figure~\ref{fig:example_2}.

@@

@@

We run \verb;pirouette; (listing~\ref{lst:pir_run}) 
and plot the results (listing~\ref{lst:pir_plot}).
The output is shown in figure~\ref{fig:example_5}.

@@
